Automated detection of data fabrication using statistical tools

### 2018-03-26 submission/redraft.rmd
Update before auto-mail

>>>>

```{r echo = FALSE}
m <- 50
sd <- 10
n <- 100

set.seed(1234)
x1_1 <- replicate(n = 10, expr = rnorm(n, m, sd))
x1_2 <- replicate(n = 10, expr = rnorm(n, m, sd))

ex1_1em <- apply(x1_1, 2, mean)
ex1_1esd <- apply(x1_1, 2, sd)
ex1_1cm <- apply(x1_2, 2, mean)
ex1_1csd <- apply(x1_2, 2, sd)
ex1_1tp <- NULL
for (i in 1:dim(x1_1)[2]) ex1_1tp[i] <- t.test(x = x1_1[,i], y = x1_2[,i], var.equal=TRUE)$p.value
ex1_1tp <- unlist(ex1_1tp)

set.seed(1234)
x2_1em <- replicate(n = 10, expr = m + runif(1, 0, 20))
x2_2cm <- replicate(n = 10, expr = m + runif(1, 0, 20))
x2_1esd <- replicate(n = 10, expr = sd + runif(1, 0, 1.5))
x2_2csd <- replicate(n = 10, expr = sd + runif(1, 0, 1.5))

sdpooled <- ((n - 1) * x2_1esd^2 + (n - 1) * x2_2csd^2)/(n * 2 - 2)
tval <- (x2_1em - x2_2cm) / sdpooled
ex2_1tp <- pt(abs(tval), n * 2 - 2, lower.tail = FALSE) * 2

# Just saving for later use in theory section
# set.seed(1234)
# std_var(n = rep(100, length(x2_1esd) * 2), sds = c(x2_1esd, x2_2csd), iter = 10000)

df <- data.frame(study = sprintf("Study %s", 1:10),
         sprintf("%s (%s)", round(ex1_1em, 3), round(ex1_1esd, 3)),
         sprintf("%s (%s)", round(ex1_1cm, 3), round(ex1_1csd, 3)),
         ex1_1tp,
         sprintf("%s (%s)", round(x2_1em, 3), round(x2_1esd, 3)),
         sprintf("%s (%s)", round(x2_2cm, 3), round(x2_2csd, 3)),
         ex2_1tp)
names(df) <- c("Study",
        "$M_E$ ($SD_E$) [S1]",
        "$M_C$ ($SD_C$) [S1]",
        "P-value [S1]",
        "$M_E$ ($SD_E$) [S2]",
        "$M_C$ ($SD_C$) [S2]",
        "P-value [S2]")
```
